In-silico molecular enrichment and clearance of the human intracranial space

### 2025-06-11 paper/main.tex
Finally Table 2 updated.

Now, to examine how CSF pulsatility affects the tracer enrichment patterns,
we consider three variations of the baseline: (i) no CSF production,
(ii) reduced pulsatility and thus decreased dispersion, and (iii) higher pulsatility with increased dispersion. We computed the reduced and increased pulsatility scenarios by halving and doubling the inflow rates associated with both cardiac and respiratory pulsations, which reduced the dispersion enhancement factors by factor of 0.25 and 4, respectively. Note that behaviour directly reflects the nature of our model: The Stokes flow is linear in its inflow boundary conditions, and the diffusion enhancement factor quadratic in the predicted pressure gradient.
Without CSF production, transport is considerably delayed
(\Cref{fig:csf}N, O). Even after $12$ hours, tracer remains in the
subtentorial regions around the cerebellum, the brain stem and in the
surrounding CSF. Interestingly, the lack of CSF production instead
allows tracer to travel upwards through the ventricular system,
reaching the third ventricle after around $12$ hours. On the other
hand, if the CSF pulsatility is reduced, we observe rapid transport
towards the upper convexity of the cranium, as in the baseline model,
but the tracer spreads exclusively within the anterior regions
(\Cref{fig:csf}P). This feature can be attributed to the CSF flow
bifurcation posterior to the ambient cistern (\Cref{fig:csf}D):
without sufficient diffusion, the tracer is unable to cross into the
posterior SAS. Indeed, with higher dispersion, the tracer moves
through the quadrigeminal cistern and further upwards into the
longitudinal fissure, with also enrichment of the cerebellum
(\Cref{fig:csf}Q).

@@

We model CSF as an incompressible Newtonian fluid at low Reynolds and
Womersley numbers via the Stokes equations with viscosity $\mu$ (see
\Cref{tab:parameters} for parameter values). To account for steady
flow induced by CSF production, we compute the CSF velocity field $\bm
u_{\rm CSF}$ and associated pressure field $p_{\rm CSF}$ in the SAS
and ventricular system $\Omega_{\rm CSF}$ that result from a steady
CSF production at a rate of $u_{\rm in}$ across the lateral ventricle
walls (\Cref{fig:csf}A--E). We allow for CSF efflux across the upper,
outer (arachnoid) boundary with efflux resistance $R_0$.

@@

We represent the evolution and distribution of a solute in the CSF
spaces $\Omega_{\rm CSF}$, brain parenchyma $\Omega_{\rm PAR}$, and
periarterial and perivenous networks $\Lambda_a \cup \Lambda_v$ via a
mixed-dimensional transport model~\cite{masri2024modelling} over a timescale
of minutes to hours (\Cref{fig:results1}A--B, \Cref{fig:csf}A--C). The
current model accounts for solute exchange between the CSF spaces,
brain parenchyma, and the PVSs, diffusion within all compartments,
dispersion and convection in the CSF spaces, and convection within the
PVS. Specifically, for $t > 0$, we solve for a concentration field
$c(x, t)$ in the 3D intracranial compartments (for $x \in \Omega_{\rm
  CSF} \cup \Omega_{\rm PAR}$) and for a cross section-averaged
concentration field $\hat{c}(s, t)$ in the perivascular networks (for
$s \in \Lambda_a, \Lambda_v$) satisfying the following equations:
\begin{subequations}
\begin{alignat}{2}
  \partial_t c - \nabla \cdot D (1 + R) \nabla c  + \nabla \cdot (\bm u_{\rm CSF} c ) + \xi (\overline{c} - \hat c ) \delta_\Gamma & = 0 && \quad \quad \mathrm{in} \quad \Omega_{\rm CSF},
  \label{eq:multi_transport_3d_CSF}
  \\ 
  \partial_t (\phi c) - \nabla \cdot D^{\ast} \nabla (\phi c)  + \nabla \cdot (\bm u_{\rm PAR} c ) + \xi (\overline{c} - \hat c ) \delta_\Gamma & = 0 && \quad \quad \mathrm{in} \quad \Omega_{\rm{PAR}},
  \label{eq:multi_transport_3d_PAR}
  \\ 
  \partial_t (A  \hat c) - \partial_s(\hat D A \partial_s ( \hat c)) +\partial_s(A \hat u \hat c )  +  \xi P (\hat c - \overline{c})  &= 0 && \quad \quad \mathrm{in} \quad  \Lambda_a, \Lambda_v .
  \label{eq:multi_transport_1d}
 \end{alignat}%
\label{eq:multi_transport}%
\end{subequations}%
In~\eqref{eq:multi_transport_3d_CSF}, $D$ is the (free) diffusion
coefficient of the solute, $R$ is the dispersion coefficient in the
CSF spaces, $\bm u_{\rm CSF}$ is the steady CSF velocity, $\xi$ is a
permeability allowing for transfer/exchange across the interfaces
$\Gamma_a, \Gamma_v$ between the periarterial and perivenous networks
and their surroundings, the overlined $\overline{c}$ denotes the
average of $c$ over cross-sections of $\Gamma_a, \Gamma_v$, and
$\delta_{\Gamma}$ is a Dirac term concentrated on $\Gamma_a,
\Gamma_v$. Additionally, in \eqref{eq:multi_transport_3d_PAR}, $\phi$
is the brain extracellular volume fraction\footnote{We set $\phi =
1.0$ in $\Omega_{\rm CSF}$ and therefore omit $\phi$
in~\eqref{eq:multi_transport_3d_CSF}.}, $D^{\ast}$ is the effective
diffusion coefficient in the parenchyma, and $\bm u_{\rm PAR}$ is an
interstitial fluid velocity. In this study, we set $\bm u_{\rm PAR} =
0$. In~\eqref{eq:multi_transport_1d}, $A = \pi (R_2^2 - R_1^2)$ is the
area and $P = 2 \pi R_2$ is the perimeter of the PVS cross-sections,
$\hat{D}$ is the effective diffusion coefficient in the PVSs, and
$\hat{u}$ is the fluid velocity (in the axial direction) in the PVS
defined for the periarterial and perivenous spaces separately
($\hat{u}|_{\Lambda_a} = \hat{u}_a$, $\hat{u}|_{\Lambda_v} =
\hat{u}_v$). Further, we model the membrane between the parenchyma and
the CSF spaces as a semi-permeable membrane with permeability
coefficient $\beta_{\rm pia}$, allowing for a jump in $c$ there. The
initial concentrations in $\Omega$ and networks $\Lambda_a, \Lambda_v$
are all set to zero.

@@

\subsection*{Intracranial influx after intrathecal injection}
To represent molecular influx into the intracranial compartments
following intrathecal injection, without modelling the spinal
compartment explicitly, we prescribe a time-dependent molecular influx
over the interface towards the spinal CSF compartment with the condition
\begin{equation*}
  (D \nabla c - \bm u c ) \cdot \bm{n} = g_{\mathrm{influx}},  \quad \mathrm{on}  \quad \Gamma_{\mathrm{SSAS}}.
\end{equation*}
Here we set
\begin{equation}
  g_\mathrm{influx}(t) = \frac{m_{\rm tot}}{T_{\rm max}^2 |\Gamma_{\rm SSAS}|} \max(0, T_{\rm max} - |t - T_{\rm max}|), 
  \label{eq:g}
\end{equation}
which expresses a hat-shaped influx function with a peak at $T_{\max}$ and a total tracer injection of $m_{\rm tot}$ (\Cref{tab:parameters}). We here consider a fixed $T_{\max} = 1.0$ h in~\eqref{eq:g}, and do not consider the effect of e.g.~reduced pulsatility on spinal transit time.

@@

in water in the PVS networks: $\hat{D} = D \equiv D^{\rm Gad}$; weighted by
the dispersion factor $R$ in the CSF spaces: $(1 + R) D$;

@@

parenchyma $D^{\ast} = D^{\rm Gad}_{\rm PAR}$. We set
$\xi$ depending on whether the PVS segment is fully embedded within
the CSF spaces ($\xi = \xi_{\rm CSF}$) or parenchyma ($\xi = \xi_{\rm
  EF}$), or neither (see also Supplementary information S1). To
account for the unresolved continuation of the perivascular network
beyond the imaging resolution limit, we implemented a permeability
gradient to avoid artificial tracer buildup. At the terminal leaf
nodes of $\Lambda_a$, permeability was increased by a factor of 100
to simulate tracer exchange with the surrounding CSF/tissue, and
linearly decreasing to the baseline value at the adjacent network
node.

@@

      Extracellular space volume fraction & $\phi$ & 0.2 & -- & \cite{nicholson1981ion} \\
      Free diffusion coefficient, Gadubutrol & $D^{\rm Gad}$ & $3.8 \times 10^{-4}$& $\text{mm}^2/\text{s}$ & \cite{valnes2020apparent}\\
      Parenchymal diffusion coefficient, Gadubutrol & $D^{\rm Gad}_{\rm PAR}$ & $1.2 \times 10^{-4}$ & $\text{mm}^2/\text{s}$  & \cite{hornkjol2022csf} \\

@@

      Molecular efflux rate & $\beta_{\rm exit}$ & $8\cdot 10^{-7}$ & m/s & $\ast$ \\

@@

      CSF outflow resistance & $R_0$ & $10^{4}$  & Pa$\cdot$s/m & $\ast$ \\ 

@@

  \caption{Model parameters. $\dagger$/$\ast$ denotes computed/estimated within this work.}

@@

@@

  \begin{tabular}{ll|llll|lll}

@@

    & Description & $R_1, R_2$ & $\xi_{\rm PVS-CSF}$ & $D|_{\Omega_{\rm CSF}}$ & $D|_{\Omega_{\rm PAR}}$ & $\mathbf{u}|_{\Omega_{\rm CSF}}$ & $\hat{u}|_{\Lambda_a}$ & $\hat{u}|_{\Lambda_v}$  \\

@@

     & baseline & $R_2 = 2 R_1$ & $\xi$ & $(1 + R) D^{\rm Gad}$ & $D^{\rm Gad}_{\rm PAR}$ & $\mathbf{u}_{\rm CSF}$ & $\hat{u}_a^p + \hat{u}_a^c$  & $\hat{u}_v^p$ \\ 
    & no CSF production & $-$ & $-$ & $-$ & $-$ & $\mathbf{0}$ & $\hat{u}_a^c$ & $0$ \\ 
    & reduced pulsatility & $-$ & $-$ & $ (1 + 0.1 R) D^{\rm Gad}$ & $-$ & $-$ & $-$  & $-$ \\ 
    & increased CSF dispersion & $-$ & $-$ & $ (1 + 10 R) D^{\rm Gad}$ & $-$ & $-$ & $-$  & $-$ \\ 
    & higher PVS flow & $-$ & $-$ & $-$ & $-$ & $-$ & $\hat{u}_a^p + \hat{u}_a^c + \hat{u}_a^v$  & $-$ \\ 
    & higher PVS exchange & $-$ & 100$\xi$  &  $-$ & $-$ & $-$ & $-$  & $-$ \\ 
    & dilated PVS in the SAS & $R_2 = 3 R_1$ & $-$ & $-$ & $-$ & $-$ & $\tilde{u}_a^p + \tilde{u}_a^c$  & $-$ \\ 

@@

  \caption{Overview of models and model variations. ($-$ denotes equal
    to the corresponding baseline value). Each PVS cross-section is
    modelled as a concentric annulus with inner radius $R_1$ and outer
    radius $R_2$ and such that $R_2 = \beta R_1$. Let $\xi$ denote the
    astrocytic endfeet permeability estimated by Koch et
    al.~\cite{koch2023estimates}. The diffusion coefficients $D^{\rm
      Gad}$ represent the (free) diffusion coefficient of Gadubutrol
    in CSF (water), and $D^{\rm Gad}_{\rm PAR}$ its effective
    diffusion coefficient in human cortical tissue, all at body
    temperature~\cite{sykova2008diffusion, valnes2020apparent}. $R$ is
    the combined cardiac and respiratory dispersion enhancement field
    (see Methods). $\mathbf{u}_{\rm CSF}$ is the CSF velocity field
    induced by CSF production in $\Omega_{\rm CSF}$, and $\hat{u}_a^p$
    and $\hat{u}_v^p$ the axial velocity induced in the periarterial
    and perivenous networks, respectively, by the corresponding
    pressure differences. $\hat{u}_a^c$ and $\hat{u}_a^v$ is the
    periarterial velocity induced by arterial pulse wave wall motion
    and slow vasomotion, respectively. Last, $\tilde{u}_a^c$ and
    $\tilde{u}_a^p$ are as $\hat{u}_a^c$ and $\hat{u}_a^p$,
    respectively, but with dilated PVS. }

>>>>

Now, to examine how CSF pulsatility affects the tracer enrichment patterns,
we consider three variations of the baseline: (i) no CSF production,
(ii) reduced pulsatility and thus decreased dispersion, and (iii) higher pulsatility with increased dispersion. We computed the reduced and increased pulsatility scenarios by halving and doubling the inflow rates associated with both cardiac and respiratory pulsations, which reduced the dispersion factors by factor of 0.25 and 4, respectively. Note that behaviour directly reflects the nature of our model: The Stokes flow is linear in its inflow boundary conditions, and the diffusion enhancement factor quadratic in the predicted pressure gradient.
Without CSF production, transport is considerably delayed
(\Cref{fig:csf}N, O). Even after $12$ hours, tracer remains in the
subtentorial regions around the cerebellum, the brain stem and in the
surrounding CSF. Interestingly, the lack of CSF production instead
allows tracer to travel upwards through the ventricular system,
reaching the third ventricle after around $12$ hours. On the other
hand, if the CSF pulsatility is reduced, we observe rapid transport
towards the upper convexity of the cranium, as in the baseline model,
but the tracer spreads exclusively within the anterior regions
(\Cref{fig:csf}P). This feature can be attributed to the CSF flow
bifurcation posterior to the ambient cistern (\Cref{fig:csf}D):
without sufficient diffusion, the tracer is unable to cross into the
posterior SAS. Indeed, with higher dispersion, the tracer moves
through the quadrigeminal cistern and further upwards into the
longitudinal fissure, with also enrichment of the cerebellum
(\Cref{fig:csf}Q).

@@

We model CSF as an incompressible Newtonian fluid at low Reynolds and
Womersley numbers via the Stokes equations with viscosity $\mu$ (see
\Cref{tab:parameters} for parameter values). To account for steady
flow induced by CSF production, we compute the CSF velocity field $\bm
u_{\rm CSF}$ and associated pressure field $p_{\rm CSF}$ in the SAS
and ventricular system $\Omega_{\rm CSF}$ that result from a steady
CSF production at a rate of $u_{\rm in}$ across the lateral ventricle
walls (\Cref{fig:csf}A--E). We allow for CSF efflux across the upper,
outer (arachnoid) boundary with efflux resistance $R_{\rm CSF, 0}$.

@@

We represent the evolution and distribution of a solute in the CSF
spaces $\Omega_{\rm CSF}$, brain parenchyma $\Omega_{\rm PAR}$, and
periarterial and perivenous networks $\Lambda_a \cup \Lambda_v$ via a
mixed-dimensional transport model~\cite{masri2024modelling} over a timescale
of minutes to hours (\Cref{fig:results1}A--B, \Cref{fig:csf}A--C). The
current model accounts for solute exchange between the CSF spaces,
brain parenchyma, and the PVSs, diffusion within all compartments,
dispersion and convection in the CSF spaces, and convection within the
PVS. Specifically, for $t > 0$, we solve for a concentration field
$c(x, t)$ in the 3D intracranial compartments (for $x \in \Omega_{\rm
  CSF} \cup \Omega_{\rm PAR}$) and for a cross section-averaged
concentration field $\hat{c}(s, t)$ in the perivascular networks (for
$s \in \Lambda_a, \Lambda_v$) satisfying the following equations:
\begin{subequations}
\begin{alignat}{2}
  \partial_t c - \nabla \cdot D (1 + R) \nabla c  + \nabla \cdot (\bm u_{\rm CSF} c ) + \xi (\overline{c} - \hat c ) \delta_\Gamma & = 0 && \quad \quad \mathrm{in} \quad \Omega_{\rm CSF},
  \label{eq:multi_transport_3d_CSF}
  \\ 
  \partial_t (\phi c) - \nabla \cdot D^{\ast} \nabla (\phi c)  + \nabla \cdot (\bm u_{\rm PAR} c ) + \xi (\overline{c} - \hat c ) \delta_\Gamma & = 0 && \quad \quad \mathrm{in} \quad \Omega_{\rm{PAR}},
  \label{eq:multi_transport_3d_PAR}
  \\ 
  \partial_t (A  \hat c) - \partial_s(\hat D A \partial_s ( \hat c)) +\partial_s(A \hat u \hat c )  +  \xi P (\hat c - \overline{c})  &= 0 && \quad \quad \mathrm{in} \quad  \Lambda_a, \Lambda_v .
  \label{eq:multi_transport_1d}
 \end{alignat}%
\label{eq:multi_transport}%
\end{subequations}%
In~\eqref{eq:multi_transport_3d_CSF}, $D$ is the (free) diffusion
coefficient of the solute, $R$ is the dispersion coefficient in the
CSF spaces, $\bm u_{\rm CSF}$ is the steady CSF velocity, $\xi$ is a
permeability allowing for transfer/exchange across the interfaces
$\Gamma_a, \Gamma_v$ between the periarterial and perivenous networks
and their surroundings, the overlined $\overline{c}$ denotes the
average of $c$ over cross-sections of $\Gamma_a, \Gamma_v$, and
$\delta_{\Gamma}$ is a Dirac term concentrated on $\Gamma_a,
\Gamma_v$. Additionally, in \eqref{eq:multi_transport_3d_PAR}, $\phi = \phi_{\rm ECS}$
is the brain extracellular volume fraction\footnote{We set $\phi =
1.0$ in $\Omega_{\rm CSF}$ and therefore omit $\phi$
in~\eqref{eq:multi_transport_3d_CSF}.}, $D^{\ast}$ is the effective
diffusion coefficient in the parenchyma, and $\bm u_{\rm PAR}$ is an
interstitial fluid velocity. In this study, we set $\bm u_{\rm PAR} =
0$. In~\eqref{eq:multi_transport_1d}, $A = \pi (R_2^2 - R_1^2)$ is the
area and $P = 2 \pi R_2$ is the perimeter of the PVS cross-sections,
$\hat{D}$ is the effective diffusion coefficient in the PVSs, and
$\hat{u}$ is the fluid velocity (in the axial direction) in the PVS
defined for the periarterial and perivenous spaces separately
($\hat{u}|_{\Lambda_a} = \hat{u}_a$, $\hat{u}|_{\Lambda_v} =
\hat{u}_v$). Further, we model the membrane between the parenchyma and
the CSF spaces as a semi-permeable membrane with permeability
coefficient $\beta_{\rm pia}$, allowing for a jump in $c$ there. The
initial concentrations in $\Omega$ and networks $\Lambda_a, \Lambda_v$
are all set to zero.

@@

\subsection*{Intracranial influx after intrathecal injection}
To represent molecular influx into the intracranial compartments
following intrathecal injection, without modelling the spinal
compartment explicitly, we prescribe a time-dependent molecular influx
over the interface towards the spinal CSF compartment with the condition
\begin{equation*}
  (D \nabla c - \bm u_{\rm CSF} c ) \cdot \bm{n} = g_{\mathrm{influx}},  \quad \mathrm{on}  \quad \Gamma_{\mathrm{SSAS}}.
\end{equation*}
Here we set
\begin{equation}
  g_\mathrm{influx}(t) = \frac{m_{\rm tot}}{T_{\rm max}^2 |\Gamma_{\rm SSAS}|} \max(0, T_{\rm max} - |t - T_{\rm max}|), 
  \label{eq:g}
\end{equation}
which expresses a hat-shaped influx function with a peak at $T_{\max}$ and a total tracer injection of $m_{\rm tot}$ (\Cref{tab:parameters}). We here consider a fixed $T_{\max} = 1.0$ h in~\eqref{eq:g}, and do not consider the effect of e.g.~reduced pulsatility on spinal transit time.

@@

in water in the PVS networks $\hat{D} = D \equiv D^{\rm Gad}$; is 
weighted by the dispersion factor $R$ in the CSF spaces: $(1 + R) D$;

@@

parenchyma $D^{\ast} = D^{\rm Gad}_{\rm PAR}$. We set $\xi$ depending
on whether the PVS segment is fully embedded within the CSF spaces
($\xi = \xi_{\rm PVS}$) or parenchyma ($\xi = \xi_{\rm EF}$), or
neither (see also Supplementary information S1). To account for the
unresolved continuation of the perivascular network beyond the imaging
resolution limit, we implemented a permeability gradient to avoid
artificial tracer buildup. At the terminal leaf nodes of $\Lambda_a$,
permeability was increased by a factor of 100 to simulate tracer
exchange with the surrounding CSF/tissue, and linearly decreasing to
the baseline value at the adjacent network node.

@@

      Extracellular space volume fraction & $\phi_{\rm ECS}$ & 0.2 & -- & \cite{nicholson1981ion} \\
      Free diffusion coefficient, Gadubutrol & $D^{\rm Gad}$ & $3.8 \cdot 10^{-4}$& $\text{mm}^2/\text{s}$ & \cite{valnes2020apparent}\\
      Parenchymal diffusion coefficient, Gadubutrol & $D^{\rm Gad}_{\rm PAR}$ & $1.2 \cdot 10^{-4}$ & $\text{mm}^2/\text{s}$  & \cite{hornkjol2022csf} \\
      %Permeability coefficient, endfoot sheath & $\xi_{\rm EF}$ & $3.8\cdot 10^{-7}$  & m/s & \cite{koch2023estimates} \\
      Permeability coefficient, PVS--CSF & $\xi_{\rm PVS}$ & $3.8\cdot 10^{-7}$  & m/s & \cite{koch2023estimates} \\

@@

      Molecular efflux rate & $\beta_{\rm exit}$ & $8.0 \cdot 10^{-7}$ & m/s & $\ast$ \\

@@

      CSF outflow resistance & $R_{\rm CSF, 0}$ & $10^{4}$  & Pa$\cdot$s/m & $\ast$ \\ 

@@

  \caption{Model parameters. $\dagger$/$\ast$ denotes
    computed/estimated within this work. The diffusion coefficients
    $D^{\rm Gad}$ represent the diffusion coefficient of Gadubutrol in
    CSF (water), and $D^{\rm Gad}_{\rm PAR}$ its effective diffusion
    coefficient in human cortical tissue, both at body
    temperature~\cite{sykova2008diffusion, valnes2020apparent,
      hornkjol2022csf}. We use the astrocytic endfeet permeability
    $\xi_{\rm EF}$ estimated by Koch et al.~\cite{koch2023estimates},
    and we set $\xi_{\rm PVS} = \xi_{\rm EF}$ as a baseline.}

@@

\newcommand{\blue}[1]{\textcolor{blue}{#1}}

@@

  \begin{tabular}{ll|lll|lll}

@@

    No. & Model description & $\bm u_{\rm CSF}$ & $\hat{u}|_{\Lambda_a}$ & $\hat{u}|_{\Lambda_v}$ & $R$ & $\xi_{\rm PVS}$ & $R_2$ \\

@@

    0 & baseline & $\bm u_{\rm CSF}$ & $\hat{u}_a^p + \hat{u}_a^c$ & $\hat{u}_v^p$                & $R_c + R_r$ & $\xi_{\rm EF}$ & $2 R_1$   \\ 
    1 & no CSF production & \blue{$\bm 0$} & \blue{$\hat{u}_a^c$} & \blue{0}                    & $R_c + R_r$ & $\xi_{\rm EF}$ & $2 R_1$   \\ 
    2 & reduced CSF pulsatility & $\bm u_{\rm CSF}$ & $\hat{u}_a^p + \hat{u}_a^c$ & $\hat{u}_v^p$  & \blue{$ R_{\rm red}$} & $\xi_{\rm EF}$ & $2 R_1$  \\ 
    3 & increased CSF pulsatility & $\bm u_{\rm CSF}$ & $\hat{u}_a^p + \hat{u}_a^c$ & $\hat{u}_v^p$  & \blue{$R_{\rm inc}$} & $\xi_{\rm EF}$ & $2 R_1$  \\ 
    4 & higher PVS flow & $\bm u_{\rm CSF}$ & \blue{$\hat{u}_a^p + \hat{u}_a^c + \hat{u}_a^v$} & $\hat{u}_v^p$  & $R_c + R_r$ & $\xi_{\rm EF}$ & $2 R_1$  \\ 
    5 & higher PVS exchange & $\bm u_{\rm CSF}$ & \blue{$\hat{u}_a^p + \hat{u}_a^c + \hat{u}_a^v$} & $\hat{u}_v^p$ & $R_c + R_r$ & \blue{100 $\xi_{\rm EF}$} & $2 R_1$   \\ 
    6 & dilated PVS in the SAS & $\bm u_{\rm CSF}$ & \blue{$\tilde{u}_a^p + \tilde{u}_a^c + \tilde{u}_a^v$} & \blue{$\tilde{u}_v^p$} & $R_c + R_r$ & $\xi_{\rm EF}$ & \blue{$3 R_1$}\\ 

@@

  \caption{Overview of model variations, with color highlighting
    changes from the baseline model. $\bm u_{\rm CSF}$ is the CSF
    velocity field induced by CSF production in $\Omega_{\rm CSF}$,
    and $\hat{u}_a^p$ and $\hat{u}_v^p$ are the axial velocities
    induced in the periarterial and perivenous networks, respectively,
    by the corresponding CSF pressure $p_{\rm CSF}$. Moreover,
    $\hat{u}_a^c$ and $\hat{u}_a^v$ are the periarterial velocities
    induced by arterial pulse wave wall motion and slow vasomotion,
    respectively. In the model variation with no CSF production, $\bm
    u_{\rm CSF} = 0$, $p_{\rm CSF} = 0$, and thus $\hat{u}_a^p =
    \hat{u}_v^p = 0$. $R_c + R_r$ is the combined cardiac and
    respiratory dispersion factor in the CSF spaces, with model
    variations $R_{\rm red}$ and $R_{\rm inc}$ corresponding to
    reduced pulsatility and increased pulsatility, respectively.  Each
    PVS cross-section is modelled as a concentric annulus with inner
    radius $R_1$ and outer radius $R_2 > R_1$. Finally,
    $\tilde{u}_a^p$, $\tilde{u}_v^p$, $\tilde{u}_a^c$ and
    $\tilde{u}_a^v$ are as $\hat{u}_a^p$, $\hat{u}_v^p$, $\hat{u}_a^c$
    and $\hat{u}_a^v$, respectively, but with a dilated PVS ($R_2 = 3
    R_1$).}
